Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\item \textit{Nips} \cite{nips}: a network of co-authors at NIPS conference from the first to the $12^{th}$ edition. Nodes are authors and links encode co-author relation between authors. This network contains 2865 nodes and 4733 links. The average degree is 3.3.

\item \textit{Condmat} \cite{condmat}: a network of co-authors for condensed matter physists. This network has 14230 nodes and 1196 links. The average degree is 0.17.

>>>>

\item \textit{Nips} \cite{nips}: nodes are authors at the NIPS conference from the first to the $12^{th}$ edition. Links encode the co-authorhip relation, i.e. if two authors have published a paper together. This network contains 2865 nodes and 4733 links with a median degree of 3.3.

\item \textit{Condmat} \cite{condmat}: nodes are scientists working in condensed matter physics, edges encode co-authorship. This network has 14230 nodes and 1196 links with a median degree of 0.17.
